Wrinkling of a confined porous layer

### 2014-11-14 fig_plis/article_plis.tex
fig:growth

>>>>

\subsection*{Characteristic time measurement}
\begin{figure}
	\includegraphics{growth}
	\caption{Growth of the instability. (a) Evolution of the gel velocity $v$, integrated over the whole surface. Inset: Evolution of the amplitude (peak to peak measurement) in semi logarithmic scale. Black line is the best exponential fit with $\tau=\SI{90}{\second}$. (b) Evolution of the bottom profile of the gel from the onset of instability (yellow) to the contact to both walls (brown). Note that the lateral size of the blister evolve in this regime. Thick black curve is the profile at much longer time. Note that blister foot (highlighted by the orange vertical line) has not moved since contact.}
	\label{fig:growth}
\end{figure}

In most of our samples, it was possible to measure directly the peak-to-peak amplitude $A(t)$ from our confocal measurements. However when the wavelength is too large compared to the field of view, this approach breaks down since we cannot observe both highest and lowest point of the surface. Even when valid, such local measurement is noisy and we prefer the measure of the vertical displacement of the gel $v$ that can be integrated over the whole field of view.

We note that when both measurements were available (as in Fig.~\ref{fig:growth}a), the characteristic time $\tau$ obtained from the fit of the exponential growth of $A(t)$ was about $4A_\text{max}/v_\text{max}$, where $A_\text{max} = e-h$ is the amplitude when the gel comes in contact with both walls. We thus used consistently this approximation of $\tau$ for all our samples. This is coherent with the fact that the blister size $\approx\lambda/2$ does not evolve after contact (see Fig.~\ref{fig:growth}b), thus the kinetic wavelength is decided when $A(t) = A_\text{max}$.

### 2014-11-14 plis_figures.tex
permeability : Figure : switch tube 1 and 2 in the sketch, use gray instead of yellow, add a second graph for glycerol 50%, use figure* Supplementary method
fig:growth

>>>>

\begin{figure*}
	\tikzsetnextfilename{permeability}
	\input{fig_plis/permeability.pgf}
	\caption{Permeability measurements. (a) Schematic representation of the experiment. (b-c) Evolution of the height of the interface in tube 1 relative to the final height in tube 2. Black line is the best exponential fit $Ae^{-t/\tau}$. (b) Gel is 4\%w casein, 4\%w GDL in water, $H=\SI{2.3}{\milli\metre}$ and $\tau=\SI{57}{\minute}$. (c) Idem in 50\%w glycerol, $H=\SI{4}{\milli\metre}$ and $\tau=\SI{100}{\hour}$.}
	\label{fig:permeability}
\end{figure*}

\begin{figure}
	\tikzsetnextfilename{growth}
	\input{fig_plis/growth.pgf}
	\caption{Growth of the instability. (a) Evolution of the gel velocity $v$, integrated over the whole surface. Inset: Evolution of the amplitude (peak to peak measurement) in semi logarithmic scale. Black line is the best exponential fit with $\tau=\SI{90}{\second}$. (b) Evolution of the bottom profile of the gel from the onset of instability (yellow) to the contact to both walls (brown). Note that the lateral size of the blister evolve in this regime. Thick black curve is the profile at much longer time. Note that blister foot (highlighted by the orange vertical line) has not moved since contact.}
	\label{fig:growth}
\end{figure}
